Data Dashboard

### 2020-02-10 analysis/05_market_simulator.Rmd
Working on how to set up matrix multiplication
Created a reactive dataframe based on user inputs

```{r load data}
intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))
intercept_mod
#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donars         -0.376
#   11. Government Grants            -0.252
#   12. Critized by Government       -0.663
#   13. Under Government Crackdown   -1.010

@@

@@

Row 
--------------------------------------------------------------------------------------
### Amnest International Expected Utility

@@

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

@@

selectInput("gp_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

@@

selectInput("ox_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

@@

selectInput("rc_funding",
            label = "Select Funding source:",
            choices = c("Handful of wealthy private donors",
                        "Government Grants",
                        "Many small private donations"))

>>>>

```{r load data}
intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))
#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donars         -0.376
#   11. Government Grants            -0.252
#   12. Critized by Government       -0.663
#   13. Under Government Crackdown   -1.011

beta <- as.data.frame(matrix(rep(0), nrow = 13))
beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human Rights", "Refugee Relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

####################################################################################

df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

})

output$data <- renderTable({
    df()
})

renderTable({
    df()
})

@@

```{r matrix multiplication, eval=FALSE, include=FALSE}
library(shiny)

beta <- data.frame(
  value = c(0,0,0),
  levels = c("Environment", "Human rights", "Refugee relief")
)

ui <- fluidPage(
  fluidRow(
    column(6,
      selectInput("ai_issue", 
                  label = "Select Issue Area:",
                  choices = beta$levels,
                  multiple = TRUE)
    ),
    column(6,
      tableOutput("data")
    )
  )
)

server = function(input, output) {

  df <- reactive({
    beta$value[beta$levels %in% input$ai_issue] <- 1
    beta
  })

  output$data <- renderTable({
    df()
  })
}
```

@@

Row 
--------------------------------------------------------------------------------------
### Amnesty International Expected Utility

@@

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

@@

selectInput("gp_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

@@

selectInput("ox_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

@@

selectInput("rc_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))
